---
title: "week_14"
author: "b06208016楊鎧綾"
date: "December 14, 2018"
output: html_document
---
##14.16
###a
```{r}
yhat=98.6-0.0138*21
```
<br/>the predicted body for 21 years old is**98.3102**

###b
```{r}
98.3-98.3102
98.4-98.3102
```
<br/> **the residual is -0.0102 and 0.0898**

###c
<br/>yhat+-T*0.7
```{r}
t=qt(0.025,df=98,lower.tail = F)
yhat-t*0.7
yhat+t*0.7
```
<br/> the interval is **(96.92,99.70)**

###d
<br/> **no, it is not unusual**, because 98.6 is in the interval

##14.28
###a
<br/>**the slope is $b_1$** because it is the information getting from sample, and not inferred 

###b
```{r}
t=qt(0.025,df=98,lower.tail = F)
low=-0.0138-t*0.0042
high=-0.0138+t*0.0042
```
<br/>**the interval is (-0.022,-0.005)**,which means under the confidence level of 95%,if we sample many times and regression the slope, it will have the  probability of 95% to be in the interval<br/>

###c
```{r}
10*low
10*high
```
<br/>**the interval is (-0.22,-0.054)**,which means under the confidence level of 95%,if we sample many times and regression the slope, it will have the  probability of 95% to be in the interval<br/>

##14.36
###a
```{r}
34.98+10.66*4
```
<br/> the yhat(fit) by this equation is **77.62**, which is the same as the table

###b
<br/>the CI on the table is **(76.670,78.571)**,which means under the confidence level of 95%, if we sample a lot of time as x=4 and calculate a mean, the mean would have the probability of 95% to be in the interval<br/>**E(y)的可能範圍**

###c
<br/>the PI on the table is **(64.307,90.934)**,which means under the confidence level of 95%,if we pick a y as x=4, it will have the  probability of 95% to be in the interval<br/>**y的可能範圍**

###d
<br/>**the prediction interval** might be better, because the tourist might want to know under the duration of last eruption, the interval the y might might contain, not the expected value, the range is too narrow, and they might want a conservative interval

##14.54
###a
<br/>there are two way to write<br/>
one is son's height=29.981+0.57568*father's height<br/>
and the other is son's height=30+0.576*father's height<br/>

###b
<br/>calculate the t-value is b1/se(b1)=7.732438 is almost equal to 7.73 which is in the table
```{r}
t_score=0.57568/0.07445
```

###c
<br/>step.1 <br/>$H_0: slope=0$ <br/>$H_a: slope \ne0$<br/>slope means the slope of regression line
<br/>step.2 the sample is bigger than 30, which is big enough
<br/>calculate the t-value is b1/se(b1)=7.732438 is almost equal to 7.73 which is in the table
```{r}
t_score=0.57568/0.07445
```
<br/>step.3 find the p-value is almost =0
```{r}
2*pt(t_score,df=71,lower.tail = F)
```
<br/>step.4 under 95% confidence level the alpha=0.05,**the p-value is smaller than alpha, so we can reject null hypothesis**
<br/>step.5 so we can say that the slope is not equal to 0

###d
<br/>slope=0.57568;se(b1)=0.07445
```{r}
t=qt(0.025,df=71,lower.tail = F)
0.57568-t*0.07445
0.57568+t*0.07445
```
<br/>**the interval of beta1=(0.427,0.724)**,which means under the confidence level of 95%,if we sample many times and regression the slope, it will have the  probability of 95% to be in the interval<br/>

##14.56
###a
```{r}
30+0.576*65
```
<br/>**the predicted height is 67.44 by the equation and 67.4 by the result**

###b
<br/>**the PI is (64.946,75.612)**,which means under the confidence level of 95%,if we pick a y as x=70, it will have the  probability of 95% to be in the interval<br/>,also means 95% of population y might be in the interval,**y的可能範圍**

###c
<br/>**the CI is (71.596,73.566)**,which means under the confidence level of 95%, if we sample a lot of time as x=74 and calculate a mean, the mean would have the probability of 95% to be in the interval<br/>**E(y)的可能範圍**

###d
<br/>the PI is more wider because it is the interval of all possible, and the CI is the interval of mean y,<br/>if looking at their function the PI is wider because it contain s and CI didn't

###e
<br/>the plot has a outlier 
<br/>如果是取樣合理的狀況下存在的離群值通常來說不可刪除，不過可將資料分段畫兩條回歸線降低誤差，若是取樣錯誤的就可直接刪除

##r studio
```{r}
#data cleaning
veh=read.csv("Vehicles.csv",sep=",",header=T)

veh=veh[,c("Vehicle","GDP")]
veh=na.omit(veh)

Vehicle=veh$Vehicle
GDP=veh$GDP

#simple linear regression
RESULTS=lm(Vehicle~GDP, data=veh)
summary(RESULTS)
```
<br/>the regression equation is **$vehicle=1606000+305.5GDP$**,<br/>which means as GDP increase 1(10億),the vehicle would predicted to sold increase 0.03055

###hypothesis test
<br/>step.1<br/>$H_0:\beta_1 = 0$<br/>$H_a:\beta_1 \ne 0$<br/>$\beta_1$ means the slope of regression line of population which is infered from sample
<br/>step.2  even though the sample is not big, it seems to be linear and donot have outlier
```{r}
plot(Vehicle~GDP,pch=16,cex=1,col="navy",
     main="Vehicle vs GDP",xlab="GDP(1 billion)",ylab="Vehicle",cex.main=2,cex.lab=1.2)
```
<br/>calculate t-score is 29.89 (by the table above)
<br/>step.3 the p-value is 2e-16(by the table above)
<br/>step.4 under the confidence level of 95% , $\alpha=0.05$, the p-value is smaller than 0.05, so we can reject $H_0$
<br/>step.5 we can say that $\beta_1$ is different from 0

###confidence interval
<br/>we knows estimated  $\beta_1=0.03055$; standard error of  $\beta_1=0.1022$(by the table above)
;degree of freedom=26-2; and assume we want to know the confidence interval under the confidence level of 95%
```{r}
t=qt(0.025,df=24,lower.tail = F)
0.03055-t*0.1022
0.03055+t*0.1022
```
<br/>the confidence interval is (-0.18,0.24),,which means under the confidence level of 95%,if we sample many times and regression the slope, it will have the  probability of 95% to be in the interval<br/>

###PI and CI
<br/>the PI means under the confidence level of 95%,if we pick a y under x=specific, it will have the  probability of 95% to be in the interval<br/>,also means 95% of population y might be in the interval,**y的可能範圍**

<br/>the CI means under the confidence level of 95%, if we sample a lot of time as x=specific and calculate a mean, the mean would have the probability of 95% to be in the interval<br/>**E(y)的可能範圍**

```{r}
#PI
PI=predict(RESULTS,data.frame(GDP=c(9000,13000,17000)),interval="prediction",level=0.95);PI

#CI
CI=predict(RESULTS,data.frame(GDP=c(9000,13000,17000)),interval="confidence",level=0.95);CI

#plotting
fit=PI[,1]
PI.low=PI[,2]
PI.high=PI[,3]

CI.low=CI[,2]
CI.high=CI[,3]

xx.test=c(9000,13000,17000)

par(mfrow=c(1,2))#把畫布分開(列，欄)

#plot PI

plot(Vehicle~GDP,data=veh,pch=20,col="gray50",
     main="Prediction interval",xlab="GDP",ylab="Vehicle",
     xlim=c(5500,18000),ylim=c(2900000,7100000),cex.main=2,cex.lab=1.2)

abline(RESULTS,col="navy")
for(i in 1:length(xx.test)){
  lines(c(xx.test[i],xx.test[i]),c(PI.low[i],PI.high[i]),col="red",lwd=3)
  points(xx.test[i],PI.low[i],col="red",pch=15)
  points(xx.test[i],PI.high[i],col="red",pch=15)
  points(xx.test[i],fit[i],col="red",pch=8)
}

#plot CI
plot(Vehicle~GDP,data=veh,pch=20,col="gray50",
     main="Confidence interval",xlab="GDP",ylab="Vehicle",
     xlim=c(5500,18000),ylim=c(2900000,7100000),cex.main=2,cex.lab=1.2)

abline(RESULTS,col="navy")
for(i in 1:length(xx.test)){
  lines(c(xx.test[i],xx.test[i]),c(CI.low[i],CI.high[i]),col="red",lwd=3)
  points(xx.test[i],CI.low[i],col="red",pch=15)
  points(xx.test[i],CI.high[i],col="red",pch=15)
  points(xx.test[i],fit[i],col="red",pch=8)
}
```

###診斷
```{r}
#draw the scatter plot
##y vs x
plot(Vehicle~GDP,pch=16,cex=1,col="navy",
     main="Vehicle vs GDP",xlab="GDP",ylab="Vehicle",cex.main=2,cex.lab=1.2)
```
<br/>by this plot we can see that it is linear, and do not have outlier
```{R}
#residuals vs x
res=RESULTS$res
plot(res~GDP,pch=16,cex=1,col="gold3",
     main="residual vs GDP",xlab="GDP",ylab="residuals",
     cex.main=2,cex.lab=1.2)

abline(h=0,col="red")
```
<br/>by this plot we can see that the deviation is almostly the same, it do not change depend on explanatory variable
```{R}
#histogram of residuals
par(mfrow=c(1,2))

hist(res,breaks=20,border="white",col="olivedrab3",
     main="histogram of residuals", xlab="residuals",
     cex.main=2,cex.lab=1.2)

#qqplot
qqnorm(res,cex.main=2,cex.lab=1.2)
qqline(res,col="red")

```
<br/>by the histogram we can se that it is almost normal distribution and do not have outlier or extreme skewed, so as the qq-plot
<br/>and we assume that two variable are independent



















