---
title: "midexam_2"
author: "b06208016楊鎧綾"
date: "November 28, 2018"
output: html_document
---

##1
###1-1
####(1)
```{r}
mu=60;sigma=6;n=36
mean=mu;mean
sd=sigma/sqrt(n);sd
```
<br/>**the sampling distribution is: mean=60, standard deviation=1**

####(2)
```{r}
z=qt((1-0.95)/2, df = 35, lower.tail = FALSE)
A=mean-z*sd;A
B=mean+z*sd;B
```
<br/>**A is 57.97, B is 62.03**,which has 95% the mean of speed will between it

####(3)
<br/>**the result is not consistent with  the belief**, because it is not in the interval calculate in part(2), which means it is out of mean for 2 standard deviation that contain 95% of sampling

###1-2
####(1)
```{r}
prop.test(x=c(0.611*131,0.426*61),n=c(131,61),alternative = "two.sided",conf.level = 0.99)
```
<br/>**the confidence interval is(-0.024,0.394)**

####(2)
```{r}
prop.test(x=c(0.611*131,0.426*61),n=c(131,61),alternative = "two.sided",conf.level = 0.95)
```
<br/>**the confidence interval is narrower in 95% confidence level**,<br/>because lower confidence level reduce the abs(z-score),which means the **margion of error will reduce** and narrow the interval

####(3)
<br/>**yes it contains 0**,<br/>**contains 0 means it may be no difference between woman and man on dating someone not attractive under 99%confidence level**

##2
###(1)
<br/>step.1<br/>null hypothesis:使用BRT-B的比例沒有比較高
<br/>alternative hypothesis:使用BRT-B的比例有比較高
<br/>$H_0$:p=0.2
<br/>$H_a$:p > 0.2
<br/>p 代表沿線居民使用BRT-B的比例

<br/>step.2 the sample is random selected and is big enough，so calculate the z-score is 1.77
```{r}
sd=sqrt((0.2*0.8)/200)
z=(0.25-0.20)/sd
z
```
<br/>step.3 the p-value is 0.039
```{r}
pnorm(z, lower.tail = FALSE)
```
```{r}
prop.test(x = 50, n = 200, 
          p = 0.2, alternative = "greater", 
          conf.level = 0.95, correct = F)
```


<br/>step.4 the p-value is smaller than $\alpha=0.05$,so it is statically significant evidence to conclude that **null hypothesis is wrong**，we can reject the null value
 <br/>step.5 so we can say that 使用BRT-B的比例有比較高, **交通局不應該建議縣長終止BRT-B的服務**
 
###(2)
<br/>step.1 <br/>null hypothesis:使用BRT-O 的比例沒有高過BRT-B
<br/>alternative hypothesis:使用BRT-O 的比例高過BRT-B
<br/>$H_0$:p1-p2=0
<br/>$H_a$:p1-p2 > 0
<br/>p1-p2 means the difference proportion of the use of BRT-O and BRT-B
<br/>step.2 the sample is random selected and is big enough，so calculate the z-score which is 1.12
```{r}
p1=60/200;n1=200
p2=50/200;n2=200
phat=(n1*p1+n2*p2)/(n1+n2)
z=(p1-p2-0)/sqrt(phat*(1-phat)*((1/n1)+(1/n2)))
z
```
<br/>step.3 the p-value is 0.13
```{r}
pnorm(z, lower.tail = FALSE)
```

```{r}
prop.test(x = c(60, 50), n = c(200,200), 
          alternative = "greater", 
          conf.level = 0.95, correct = F)
```

<br/>step.4 the p-value is larger than 0.05,so it is not statically significant evidence to conclude null hypothesis is wrong，we cannot reject the null value

<br/>step.5 so we can say that 使用BRT-O 的比例沒有高過BRT-B,兩者幾乎無差別,**交通局不應該建議縣長實現BRT-O的服務**

###(3)
<br/>因為$\alpha=0.05$,而此題為單尾檢定所以如果要計算信賴區間，他的信心水準是90%
```{r}
brt_b=prop.test(x=50,n=200,alternative = "two.sided",conf.level = 0.90)
brt_b$conf.int
brt_o=prop.test(x=60,n=200,alternative = "two.sided",conf.level = 0.90)
brt_o$conf.int
```


```{r}
plot(c(0,3),type='n',xlim=c(0.1,0.4),xlab='proportion of using',ylab='',axes=F,
     main='Comparsion of the two confidence interval')

lines(c(0.2008983,0.3061036),c(2,2))
text(0.18,2,labels='brt_b')
lines(c(0.2008983,0.2008983),c(1.95,2.05))
lines(c(0.3061036,0.3061036),c(1.95,2.05))
lines(c(0.25,0.25),c(1.95,2.05))

lines(c(0.2473182,0.3582691),c(1,1))
text(0.23,1,labels='brt_o')
lines(c(0.2473182,0.2473182),c(0.95,1.05))
lines(c(0.3582691,0.3582691),c(0.95,1.05))
lines(c(0.3,0.3),c(0.95,1.05))

axis(1)
```
<br/>**兩者的信賴區間大量重疊，因此可能是無差別的，與第2小題假說檢定的結果一致，BRT_O的預計使用率並沒有比較高**

##3
###(1)
<br/>step.1 <br/>null hypothesis:使用大眾運輸的通勤時間沒有較長
<br/>alternative hypothesis:使用大眾運輸的通勤時間較長
<br/>$H_0:\mu_1-\mu_2=0$
<br/>$H_a:\mu_1-\mu_2 > 0$
<br/>$\mu_1$ 代表使用大眾運輸的通勤時間;$\mu_2$ 代表開車的通勤時間
<br/>step.2 the sample size is big enough to continue hypothesis test, the t-score=2.236(unpooled,unpooled is better all the time)
```{r}
se=sqrt((20^2/100)+(10^2/100))
t_score=((35-30)-0)/se;t_score
```
<br/>step.3 the p-value=0.013;df是取n1-1與n2-1較小者
```{r}
pt(t_score,df=99,lower.tail = F)
```

<br/>step.4 set alpha=0.05,the p-value is smaller than alpha, so we can reject null hypothesis
<br/>step.5 we can say that 使用大眾運輸的通勤時間較長
<br/>**交通局可說在台北使用大眾運輸的通勤時間較長**

###(2)
<br/>step.1 <br/>null hypothesis:使用大眾運輸的通勤時間沒有變短
<br/>alternative hypothesis:使用大眾運輸的通勤時間有變短
<br/>$H_0:\mu_d=0$
<br/>$H_a:\mu_d < 0$
<br/>$\mu_d$ 代表計畫完成前後使用大眾運輸的通勤時間差
<br/>step.2 the sample size is big enough to continue hypothesis test, the t-score=-2
```{r}
mud=-1
s=5
t_score=(-1-0)/(5/sqrt(100));t_score
```
<br/>step.3 the p-value=0.024
```{r}
pt(t_score,df=99)
```
<br/>step.4 set alpha=0.05,the p-value is smaller than alpha, so we can reject null hypothesis
<br/>step.5 we can say that 使用大眾運輸的通勤時間有變短
<br/>**交通局可說計畫減少了在台北使用大眾運輸的通勤時間**

###(3)
####由顯著水準
<br/>step.1 <br/>null hypothesis:計畫後使用大眾運輸的通勤時間與開車的時間無差異
<br/>alternative hypothesis:計畫後使用大眾運輸的通勤時間與開車的時間有差異
<br/>$H_0:\mu_3-\mu_2=0$
<br/>$H_a:\mu_3-\mu_2 \neq 0$
<br/>$\mu_3$ 代表計畫完成後使用大眾運輸的通勤時間;$\mu_2$ 代表開車的通勤時間
<br/>step.2 the sample size is big enough to continue hypothesis test, the t-score=1.77(unpooled)
```{r}
se=sqrt((10^2/100)+(10^2/100))
t_score=((32.5-30)-0)/se;t_score
```
<br/>step.3 the p-value=0.080
```{r}
2*pt(t_score,df=99,lower.tail = F)
```
<br/>step.4 set alpha=0.05,**the p-value is LARGER than alpha, so we cannot reject null hypothesis**
<br/>step.5 we can say that 計畫後使用大眾運輸的通勤時間與開車的時間無差異
<br/>**交通局可說計畫使使用大眾運輸的通勤時間與開車的時間無差異**

####由效應值
```{r}
se=sqrt((10^2/100)+(10^2/100))
t_score=((32.5-30)-0)/se
dhat=t_score*sqrt((1/100+1/100))
dhat
```
<br/>**由於dhat=0.25最接近0.2,可以說幾乎看不出差別(effect size is small),交通局可說計畫使使用大眾運輸的通勤時間與開車的時間無差異**

##4
###(1)
####資料準備
```{r}
data<-read.csv("pennstate2.csv")
```
```{r}
str(data)
str(data[data$t=="Y",])
```

####hypothesis test
<br/>step.1 <br/>null hypothesis:沒有超過20%的同學運動量達標
<br/>alternative hypothesis:有超過20%的同學運動量達標
<br/>$H_0$:p=0.2
<br/>$H_a$:p > 0.2
<br/>p means the proportion of the students that exercise good
<br/>step.2 the sample is random selected and is big enough，so calculate the z-score which is -1.75
```{r}
phat=31/205;n=205
z=(phat-0.2)/sqrt(0.2*0.8/n)
z
```
<br/>step.3 the p-value is 0.9596
```{r}
pnorm(z,lower.tail = F)
```

```{r}
prop.test(x = 31, n = 205, 
          p = 0.2, alternative = "greater", 
          conf.level = 0.95, correct = F)
```

<br/>step.4 the p-value is larger than 0.05,so it is not statically significant evidence to conclude null hypothesis is wrong，we cannot reject the null value

<br/>step.5 so we can say that 沒有超過20%的同學運動量達標,**校方不可說有超過20%的同學達標**

###(2)
####資料準備
```{r}
b<-data[data$s=="F",]
str(b)
str(b[b$t=="Y",])
p_f=18/137
c<-data[data$s=="M",]
str(c)
str(c[c$t=="Y",])
p_m=13/68
```
####hypothesis test
<br/>step.1 <br/>null hypothesis:男生運動量達標的比例沒有比女生高
<br/>alternative hypothesis:男生運動量達標的比例比女生高
<br/>$H_0$:p1-p2=0
<br/>$H_a$:p1-p2 > 0
<br/>p1-p2 means the difference proportion of 男女運動達標比例;p1為男生運動達標比例;p2為女生運動達標比例
<br/>step.2 the sample is random selected and is big enough，so calculate the z-score which is 1.125
```{r}
p1=13/68;n1=68
p2=18/137;n2=137
phat=(n1*p1+n2*p2)/(n1+n2)
z=(p1-p2-0)/sqrt(phat*(1-phat)*((1/n1)+(1/n2)))
z
```
<br/>step.3 the p-value is 0.13
```{r}
pnorm(z, lower.tail = FALSE)
```
```{r}
prop.test(x = c(13,18), n = c(68,137), 
          alternative = "greater", 
          conf.level = 0.95, correct = F)
```

<br/>step.4 the p-value is larger than 0.05,so it is not statically significant evidence to conclude null hypothesis is wrong，we cannot reject the null value

<br/>step.5 so we can say that 男生運動量達標的比例沒有比女生高,**此調查結果無法支持校方宣稱**




