---
title: "homework1"
author: "b06208016 楊鎧綾"
date: "September 13, 2018"
output: html_document
---

##3.1
Compute the difference between 2018 and the year
you started at this university and divide this by
the difference between 2018 and the year you were
born. Multiply this with 100 to get the percentage
of your life you have spent at this university. 
```{r}
((2018-2017)/(2018-1999))*100
```

##3.2
Repeat the previous ToDo, but with several steps
in between. You can give the variables any name
you want, but the name has to start with a letter.
```{r}
freshman=2017#the year I started at this university
born=1999#the year I were born
percentage=((2018-freshman)/(2018-born))*100#the percentage of my life I have spent at this university
percentage
```

##3.4
Compute the sum of 4, 5, 8 and 11 by first combining
them into a vector and then using the function
sum.
```{r}
numbers<-c(4,5,8,11)
sum(x=numbers)
```

##3.5
Plot 100 normal random numbers.
```{r}
plot(rnorm(100))
```

##4
Find help for the sqrt function.
```{r}
help(sqrt)#=?sqrt
```

##5
Make a file called firstscript.R containing Rcode
that generates 100 random numbers and plots
them, and run this script several times.
```{r}
source("firstscript.R")
source("firstscript.R")
source("firstscript.R")
```

#6.2
Put the numbers 31 to 60 in a vector named P and
in a matrix with 6 rows and 5 columns named Q.
Tip: use the function seq. Look at the different
ways scalars, vectors and matrices are denoted in
the workspace window.
```{r}
P<-seq(from=31,to=60,by=1)
P
Q<-matrix(data=P,nrow=6,ncol=5)#by colume
Q
Q2<-matrix(data=P,nrow=6,ncol=5,byrow=TRUE)#by row
Q2
```

##6.3
Make a script file which constructs three random
normal vectors of length 100. Call these vectors x1,
x2 and x3. Make a data frame called t with three
columns (called a, b and c) containing respectively
x1, x1+x2 and x1+x2+x3. Call plot(t) for this
data frame.
```{r}
x1<-rnorm(100)
x2<-rnorm(100)
x3<-rnorm(100)
t=data.frame(a=x1,b=x1+x2,c=x1+x2+x3)
t
plot(t)
```

##7
Add these lines to the script file of the previous
section. Try to find out, either by experimenting
or by using the help, what the meaning is of rgb,
the last argument of rgb, lwd, pch, cex
```{r}
plot(t$a, type="l", ylim=range(t),
lwd=3, col=rgb(1,0,0,0.3))
lines(t$b, type="s", lwd=2,
col=rgb(0.3,0.4,0.3,0.9))
points(t$c, pch=20, cex=4,
 col=rgb(0,0,1,0.3))
```

###lwd=線條寬度
###col(rgb)=線條顏色及深淺
###pch=點(圖型)的樣式
###cex=點的大小,
###type=圖表形式,ylim=y軸座標最小值

##8
Make a file called tst1.txt in Notepad from the
example in Figure 4 and store it in your working
directory. Write a script to read it, to multiply the
column called g by 5 and to store it as tst2.txt
```{r}
d = data.frame(a = c(1,2,4,8,16,32), g = c(2,4,8,16,32,64),x=c(3,6,12,24,48,96))
d
write.table(d, file="tst1.txt",row.names=FALSE)
d2 = read.table(file="tst1.txt",header=TRUE)
d2$g=d2$g*5
write.table(d2, file="tst2.txt",row.names=FALSE)
d2
```

##9
Compute the mean of the square root of a vector
of 100 random numbers. What happens?
```{r}
a=rnorm(100)
a
b=sqrt(a)
b
c=mean(b)
c
```

##10.2
Make a graph with on the x-axis: today, Sinterklaas2017 and your next birthday and on the y-axis the
number of presents you expect on each of thesedays. Tip: make two vectors first.
```{r}
x=strptime(c("20180913","20171205","20190802"),format="%Y%m%d")
y=c(0,7,5)
plot(x=x,y=y,pch=20,cex=2)
```

##11.2
Make a vector from 1 to 100. Make a for-loop
which runs through the whole vector. Multiply
the elements which are smaller than 5 and larger
than 90 with 10 and the other elements with 0.1
```{r}
h=seq(from=1,to=100)
s=c()
for (i in 1:length(h))
{
  if(h[i]<5|h[i]>90)
  {
    s[i]=h[i]*10
  }else{
    s[i]=h[i]*0.1
  }
}
s
```

##11.3
Write a function for the previous ToDo, so that you
can feed it any vector you like (as argument). Use
a for-loop in the function to do the computation
with each element. Use the standard R function
length in the specification of the counter.
```{r}
fun1=function(h)
{
  s=c()
  for (i in 1:length(h))
  {
    if(h[i]<5|h[i]>90)
    {
      s[i]=h[i]*10
    }else{
      s[i]=h[i]*0.1
    }
  }
  return(s)
}
#test
h=seq(from=-5,to=100)
fun1(h)
```


















