---
title: "lab_9"
author: "b06208016楊鎧綾"
date: "November 9, 2018"
output: html_document
---
##11.18
###a
```{r}
2/sqrt(100)
```
```{r}
2/sqrt(64)
```
<br/>**the standard error of the mean of women is 0.2**<br/>which is smaller than the standard error of the mean of men, which is 0.25 is because **the sample of the women is bigger than the men**<br/>the bigger the sample size the smaller the standard error if standard deviation is the same<br/>

###b
```{r}
sqrt((2^2)/100+(2^2)/64)
```
<br/>**standard error of difference between women and men is 0.3201562**<br/>

##11.32
###a
```{r}
xbar1=4.5
se1=1.6/sqrt(25)
t1=2.06 #以n-1=24,根據查表得知
ci.lower=xbar1-t1*se1
ci.high=xbar1+t1*se1
ci.lower;ci.high
```
<br/>**the confidence interval under 95% confidence level of the df=24 is (3.8408,5.1592)**<br/>

###b
```{r}
xbar2=8.1
se2=1.8/sqrt(23)
t2=2.07 #以df=22,根據查表得知
ci.lower2=xbar2-t2*se2
ci.high2=xbar2+t2*se2
ci.lower2;ci.high2
```
<br/>**the confidence interval under 95% confidence level of the df=22 is (7.323075,8.876925)**<br/>

###c
```{r}
plot(c(0,3),type='n',xlim=c(3,9),xlab='Mean day of duration of symptom',ylab='',axes=F,
     main='Comparsion of the two confidence interval')

lines(c(3.84,5.16),c(2,2))
text(3.5,2,labels='zinc')
lines(c(3.84,3.84),c(1.95,2.05))
lines(c(5.16,5.16),c(1.95,2.05))
lines(c(4.5,4.5),c(1.95,2.05))

lines(c(7.32,8.88),c(1,1))
text(6.9,1,labels='placebo')
lines(c(7.32,7.32),c(0.95,1.05))
lines(c(8.88,8.88),c(0.95,1.05))
lines(c(8.1,8.1),c(0.95,1.05))

axis(1)
```

###d
<br/>**從ab小題的信賴區間來看，兩者的感冒持續時間的信賴區間沒有交集，c小題畫圖呈現就更加明顯沒有交集了，而且zinc的整個信賴區間數字都比placebo小，所以可以說明用zinc是比較有效可以減少感冒持續時間的**<br/>

###e
<br/>在連續資料的信賴區間預估中，必須符合以下其中一個條件<br/>1.random selected and normal distribution<br/>2.random selected sample bigger than 30<br/>**而此題不管是zinc還是plavebo的抽樣樣本數小於30，因此必需要是常態分部，才可以這樣估計出信賴區間**<br/>

##11.50
###a
```{r}
dbar=1.8
se=2.1/sqrt(20)
t=2.09 #以df=19,confidence level is95%,根據查表得知
ci.lower=dbar-t*se
ci.high=dbar+t*se
ci.lower;ci.high
```
<br/>**the confidence interval for the mean difference of desired and actual height under 95% confidence level of the df=19 is (0.82,2.78)<br/>which means there are 95% the randomly selected sample mean will be in the interval, or 95% the sampling confidence interval will contain the population parameter**<br/>

###b
<br/>**因為此題樣本數為20小於30，因此母體資料必需要是常態分部，而且樣本資料不可有嚴重的skewed或者有outline，才可以這樣估計出信賴區間**<br/>

###c
<br/>**the confidence interval for the mean difference of desired and actual height under 95% confidence level of the df=19 is (0.82,2.78)<br/>which means there are 95% the randomly selected sample mean will be in the interval, or 95% the sampling confidence interval will contain the population parameter<br/>does not mean all the women between the age want to be taller<br/>那樣的說法太肯定，誤解了信心水準與信賴區間的意義**<br/>

###d
<br/>**此題不適用approximate 95% interval confidence intervals，因為樣本數不夠大<br/>如果是使用查表的話t值是2.09,但用approximate的話t值是2,會造成信賴區間的估計較窄，造成估計上並不是比較保守**<br/>

##11.60
###a
```{r}
exer_t<-c(62,72,60,63,75,64,60,52,64,80,68,64)
exer_f<-c(72,84,66,72,62,84,76,60)
t.test(exer_f,exer_t,alternative="two.sided",paired = F,var.equal = F,conf.level = 0.95)
```
<br/>**the 95% confidence interval for the difference in mean is(-15.06,1.73)<br/>because the sample size is smaller than 30, so the distribution must be normal distribution, if want to calculate the confidence interval **<br/>

###b
```{r}
t.test(exer_f,exer_t,alternative="two.sided",paired = F,var.equal = T,conf.level = 0.95)
```
<br/>**the 95% confidence interval for the difference in mean is(-14.50,1.17)<br/>because the sample size is smaller than 30, so the distribution must be normal distribution, if want to calculate the confidence interval **<br/>

###c
```{r}
sd(exer_t)
sd(exer_f)
```
<br/>**此題standard deviation 較大的分組裡的個體數卻較少，因此是不適合用pooled procedure 的,而且用pooled procedure 的時候兩個分組的standard deviation要非常接近誤差才會比較小<br/>而且一般不建議使用pooled procedure，除非兩個分組的standard deviation要非常接近以及standard deviation 較大的分組裡的個體數較多才使用，而且他是較保守的估計**<br/>

##11.78
###a
```{r}
sqrt(22.64^2/16+12.04^2/16)
```
<br/>**the unpooled standard error for the difference in the two sample means is 6.410593**<br/>

###b
```{r}
t=2.07 #藉由查表df=22 under 95%confidence level
se=sqrt(22.64^2/16+12.04^2/16)
mean=113.75-99.87
ci.lower=mean-t*se
ci.high=mean+t*se
ci.lower;ci.high
```
<br/>**the confidence interval under 95% confidence level of the df=22 is (0.610729,27.14993)**<br/>

###c
<br/>**we can conclude that the population means for the two groupes are different, because the confidence interval is all above 0, and those who drink alcohol expected to use longer time <br/>if the interval do not contain 0, we can infer that two groups are different**<br/>

###d
<br/>if we want to use unpooled procedure we need to make sure the two groups are independent and have at least one of the two conditions<br/>1.bell-shape randomly selected samples<br/>2.sample size is above 30<br/>**the sample size of this case is both 16 which is below 30,and we do not know whether the sample and population is bell-shape, so we cannot verify the nessary conditions**<br/>

##11.80
###a
<br/>**it is paired data because the two groups are not independent, and we want to know the mean of the difference not the difference of the mean**<br/>

###b
<br/>**because we need to random selected, and there are some other conditions can affect the outcom ,such as 對於實驗的熟悉度，第一次較不熟悉，後面會慢慢抓到技巧，因此如果規定先用慣用手，可能會導致資料收集的誤差**<br/>

###c
```{r}
d<-c(22,19,18,17,15,16,16,20,17,15,17,17,14,20,26)
nd<-c(18,15,13,16,17,16,14,16,20,15,17,17,16,18,25)
t.test(d,nd,alternative="two.sided",paired = T,var.equal = F,conf.level = 0.90)
```
<br/>**the 90%confidence interval of the differences is(-0.04018838,2.17352171)**<br/>

###d
<br/>**因為信賴區間涵蓋0，所以用慣用手和用非慣用手可以說是沒有差別的**<br/>

##r studio
```{r}
Simd_CI<-function(n,mu1 ,sd1,mu2 ,sd2,m,conf.level){
  
  prob<-(1-conf.level)/2
  t.value=qt(prob,df=n-1,lower.tail=FALSE)
  
  mean.x=c()
  se.x=c()
  
  CI.half=c()
  CI.Up=c()
  CI.Lower=c()
  Check=c()
  
  #Mumeanltiple sampling
  for (i in 1:m){
    
    #one sampling
    x1<-rnorm(n,mean=mu1,sd=sd1)
    x2<-rnorm(n,mean=mu2,sd=sd2)
    mean.x[i]<-mean(x1-x2)
    se.x[i]<-sqrt((sd(x1)^2)/n+(sd(x2)^2)/n)
    
    #calculate one confidence interval
    CI.half[i]<-t.value*se.x[i]
    CI.Up[i]<-mean.x[i]+CI.half[i]
    CI.Lower[i]<-mean.x[i]-CI.half[i]
    if(CI.Up[i]>(mu1-mu2) & CI.Lower[i]<(mu1-mu2)) Check[i]<-1 else Check[i]<-0
  }
  
  plot(c(CI.Up,CI.Lower),type="n",pch=19,xlim=c(1,m),xlab="Trial",ylab=expression(mu[d]))  #n=甚麼都不畫
  abline(h=mu1-mu2,col="blue")
  
  #check weather each confidence interval captures the population mean (mu)
  for (i in 1:m){
    if (Check[i]==1){
      points(i, mean.x[i], col="green", pch=10)
      points(i, CI.Up[i], col="green", pch=20)
      points(i, CI.Lower[i], col="green", pch=20)
      lines(c(i,i),c(CI.Lower[i],CI.Up[i]), col="green", pch=19)
      
    }else{
      points(i, mean.x[i], col="red", pch=10)
      points(i, CI.Up[i], col="red", pch=20)
      points(i, CI.Lower[i], col="red", pch=20)
      lines(c(i,i),c(CI.Lower[i],CI.Up[i]), col="red", pch=19)
    }
  }
  
  
  title(expression(paste("Simulating confidence interval for",mu[d])))
  
  legend("bottomright",cex=0.6,bty = "n",ncol = 2,
         c(expression(paste(mu[d],"Captured")),expression(paste(mu[d],"Not Captured"))),
         fill = c("green","red"))
  
  No.Captured = m-sum(Check)
  RESULT = list(Trial=m, Sample.Size=n,
                Population.mean=c(mu1,mu2), Population.sd=c(sd1,sd2),
                Confidence=conf.level,
                No.Captured=No.Captured)
  
  return(RESULT)
}
```
```{r}
Simd_CI(n=30, m=100, mu1=50 ,mu2=45, sd1=5, sd2=10, conf.level=0.95)
```

