---
title: "week16"
author: "b06208016楊鎧綾"
date: "December 28, 2018"
output: html_document
---

##16.8
###a
<br/>$H_0:$ no mattter what age it is the number of children couple average wants is the same
<br/>$\mu_1=\mu_2=\mu_3=\mu_4$
<br/>$H_a:$ the number of children couple wants is different according to age
<br/>$\mu_1\neq\mu_2\neq\mu_3\neq\mu_4$ (at least one of them is different from others)
<br/>$\mu$ means the ideal number of children a couple want, and the age range is  18~29, 30~44, 45~59, 60~89, respectively<br/>
<br/>the sample is from US adults from age 18~89, so the population it can infer might be US adults from age 18~89, better not overestimate

###b
<br/> F-statistic: 7.41; p-value: 0
<br/>under the confidence level of 95% $\alpha=0.05$, the p-value=0 is smaller than $\alpha$, so we can reject the null hypothesis, <br/>we can say that the number of children couple wants is different according to age

###c
<br/>從信賴區間我們可以看到18-29歲及60-89歲的信賴區間大量重疊，而30-44歲及45-59歲的也大量重疊，前兩組的信賴區間高於後兩組，而且他們並無重疊<br/><br/>我們可以說18-29歲及60-89歲是無差別的，30-44歲及45-59歲的也是無差別的，但是18-29歲及60-89歲想要的孩子較多，他們與30-44歲及45-59歲是有差別的

###d
```{r}
0.8198*2>0.9903
```
<br/>the max standard deviation is smaller than two times of min sd, so it is reasonable to assume equal sd

##16.24
###a
```{r}
d1=c(7,2,5,6)
d2=c(8,12,0,4)
d3=c(16,9,5,10)
x1=mean(d1)
x2=mean(d2)
x3=mean(d3)
xbar=(x1+x2+x3)/3
xbar;x1;x2;x3
```
<br/>xbar=7; x1=5; x2=6; x3=10

###b
```{r}
ssg=length(d1)*(x1-xbar)^2+length(d2)*(x2-xbar)^2+length(d3)*(x3-xbar)^2
ssg
```
<br/> SS Group = 56 

###c
```{r}
all=c(d1,d2,d3)
sst=0
for (i in all){
  sst=sst+((i-xbar)^2)
}
sst
```
<br/> SS Total=212

###d
```{r}
sse=sst-ssg
sse
```
<br/>SS Error = 156

###e
```{r}
msg=ssg/(3-1)
mse=sse/(length(all)-3)
f_score=msg/mse;f_score
```
<br/>the f-statistic is 1.615, and the degree of freedom is 2 and 9

##16.36
###a
<br/>男生坐越前面睡越少，坐越後面則睡越多，而且睡覺時數差異頗大

###b
<br/>女生坐越前面睡越多，坐越後面則睡越少，但睡覺時數差異不大

###c
<br/>因為兩條線沒有平行，所以可以說性別與座位有交互作用，所坐座位對於不同性別來說影響到平均睡眠時間程度不一

##16.52
###a
```{r}
load("wineratings.rdata")
# data distribution
boxplot(q ~ r, data = wineratings, 
        main = "quality among regions", cex.main = 1.6)

#install.packages("ggpubr")
library(ggpubr)

# visualize std for each group
ggline(wineratings, x = "r", y = "q", add = c("mean_sd"), 
       color = "firebrick3", main = "Std among groups",
       ggtheme = theme_gray())
```
<br/>the data of region 3 is higher than other two, the quality of region 3 is different from the other two, and region 1 and two might be no difference

###b
```{r}
# mean and sd for each group
stu.mean = tapply(wineratings$q, wineratings$r, mean)
stu.sd = tapply(wineratings$q, wineratings$r, sd)
stu.n = tapply(wineratings$q, wineratings$r, length)

stu = data.frame(n = stu.n, mean = stu.mean, sd = stu.sd)
stu
```
<br/>the mean and sd is as the dataframe shows

###c
<br/>step.1 
<br/>$H_0:$ there are no difference between regions, that is $\mu_1 = \mu_2 = \mu_3$
<br/>$H_a:$ there are difference between regions, that is $\mu_1 \neq \mu_2 \neq \mu_3$(at least one of them is different from others)
<br/>$\mu$ means the mean of the quality of a region 
<br/>step.2 as the boxplot shows the data do not have outlier and extreme skewed, <br/>and the max sd is smaller than two times the min sd, we can calculate the f-value which is 27.52
<br/>step.3 as the data shows the p-value is 6.59e-08
```{r}
oneway = aov(q ~ factor(r), data = wineratings)
summary(oneway)
```
<br/>step.4 under 95% confidence level $\alpha=0.05$, the p-value is smaller than alpha, so we can reject $H_0$
<br/>step.5 we can say that depend on different rejions the quallity of wine might be different






