---
title: "homework3"
author: "b06208016楊鎧綾"
date: "September 29, 2018"
output: html_document
---

#7.14
##a
because there is six sides and is equally likely
```{r}
1/6
```

##b
because there is six sides and is equally likely
```{r}
(1/6)*2
```

##c
because there is six sides and is equally likely,odd number is 1,3,5
```{r}
(1/6)*3
```

#7.32
##a
```{r}
22/190 #pick 3/total
```

##b
```{r}
(2+6)/190 #(pick 1 + pick 10)/total
```

##c
```{r}
(2+22+18+56+14)/190 #(pick 1 + pick 3 + pick 5 + pick 7+ pick 9)/total
```

# 7.48
## a
P(A)=0.55<br/>
P(AC)=0.45<br/>
P(B|A)=0.8<br/>
P(B|AC)=0.1<br/>

##b
P(A and B)=P(A)*P(B|A)<br/>
which means those who are republicans and vote for candidate X
```{r}
b=0.55*0.8
b
```

##c
P(AC and B)=P(AC)*P(B|AC)<br/>
which means those who are NOT republicans but vote for candidate X
```{r}
c=0.45*0.1
c
```

##d
P(B)=P(A and B)+P(AC and B)<br/>
means those vote for candidate X
```{r}
b+c
```

##e
P(B) means the percentage candidate X receive of all of voter, which is 48.5%

#7.66
A=voter is woman<br/>
B=voter is democrat<br/>
P(A and B)=0.2<br/>
P(A)=0.5<br/>
P(B|A)=P(A and B)/P(A)
```{r}
0.2/0.5
```

#7.72
##a
```{r}
aa=0.25^3
aa
```

##b
```{r}
bb=0.4^3
bb
```

##c
aa means who just guess can enter second experiment<br/>
bb means who have ESP can enter second experiment
```{r}
0.5*bb/(0.5*aa+0.5*bb)
```

#7.76
#a
```{r}
50/10000
```

##b
I think it is a good idea because the probability of an accident with a stoplight is 0.01，<br/>
but the probability of an accident without a stoplight is 0.005<0.01

#r 程式練習
```{r}
# Build a simulation function 

SimProb = function(n,m) {
  
  # Settings
  all = 0
  
  #模擬n次
  for (i in 1:n) {
    
    # Step1: 每次模擬抽m 包 
    f.samp = sample(x = 1:4, size = m, replace = T)
    
    # Step2: 看有幾次全部都有
    if (1%in%f.samp & 2%in%f.samp & 3%in%f.samp & 4%in%f.samp) {
      all = all + 1
    }
    
  }
  
  # Step3: Preparing the output message 
  return(all/n)
}




# 實測 ------------------------------------------------------------------

SimProb(1000,4)

sample=c()
for (i in 1:10){
  sample[i]=SimProb(1000,4)
}
sample

```




